---
title: "Analysis"
author: "Pedro Girardi"
date: "January 27, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages}
library(tidyverse)
library(data.table)
library(lme4)
library(plm)
library(lmtest)
library(sandwich)
library(car)
```

## Importing df

```{r}
complete.df = fread("complete.csv")
```

## Recoding Variables

Variables:

v203: Gender (Male=1)
v208: Ethnicity (White=1, Black=2, Yellow=3, Mixed=4, Native=5, Ignored=9)
v4191: Income (999999999 = ignored)
v301: Writes/reads? (Yes=1, No=2, 0="Deleted by the surveyer", NA=NA)
v307: schooling (a mess...)/turn into factor
v234: age

ADD 409 (TYPE OF WORKER!!!!)

```{r}
complete.df = complete.df %>% mutate(Gender = as.factor(v203),
                       Ethnicity = as.factor(v208),
                       Literacy = as.factor(v301),
                       Schooling = as.factor(v307),
                       EmploymentType = as.factor(v409),
                       v035 = as.factor(v035),
                       idind = as.factor(idind)) %>% 
                              select(-v040, -v050, -v203, -v208, -v301, -v307, -v409,
                                     -starts_with("vD"))
complete.df$Schooling = as.factor(ifelse(is.na(complete.df$Schooling), "NoSchooling", complete.df$Schooling))
levels(complete.df$Gender) = c("Male", "Female")
levels(complete.df$Ethnicity) = c("White", "Black", "Yellow", "Mixed", "Native", "Ignored")
levels(complete.df$Literacy) = c("Yes", "No")
levels(complete.df$Schooling) = c("Primary", "HighSchool_1", "HighSchool_2",
                                  "MiddleSchool", "HighSchool_3", "College",
                                  "AdultsSchool", "PreSchool", "Graduate",
                                  "NoSchooling")
levels(complete.df$EmploymentType) = c("Domestic", "Employee") #note that people who own their own business don't report income
```

## Visually checking for mixed effects

```{r, cache=T, eval=F}
set.seed(2)
ggplot(complete.df %>% filter(idind %in% sample(complete.df$idind, size = 25)),
       aes(x=lagInflationTax, y=realWage)) +
  geom_point(aes(col=idind)) +
  geom_smooth(aes(col=idind), method = "lm", se = F) +
  theme_minimal() +
  theme(legend.position="none")
```

## Fitting LME model

Worrying about LME not being the ideal. Needs to test with Hausman test.


```{r}
set.seed(1)
sampleInd = sample(complete.df$idind, size = length(complete.df$idind)/100)
sample_complete.df =  complete.df %>% filter(idind %in% sampleInd)
```

## be sure to test with hausman 

* remove people w fewer than 3 

* run hausmann test 

Decided not to have random effects for inflation coefficient so to avoid issues with hausmann test (trade-off)

Checked with Katie, sampling expert, on potential issues with subsetting and decided to subset (issue with power may exist, but mostly for very specific interactions)


```{r Fitting fixef}
fixed = plm(log(realWage) ~ lagInflationTax + ChangeInGDP * lagChangeInGDP + 
                (v035 +Gender + Ethnicity + Literacy +
                   Schooling + EmploymentType +
                   v234 + I(v234^2) + as.factor(v070)+
                   veryVulnerable)*lagInflationTax,
            data = complete.df, index = c("idind"), model = "within") 

# random = plm(log(realWage) ~ lagInflationTax + ChangeInGDP * lagChangeInGDP + 
#                 (v035 +Gender + Ethnicity + Literacy +
#                    Schooling + EmploymentType +
#                    v234 + I(v234^2) + as.factor(v070)+
#                    veryVulnerable)*lagInflationTax,
#             data = complete.df, index = c("idind"), model = "random") 
```

```{r}
summary(fixed)
# summary(random)
```

```{r, eval=F}
phtest(fixed, random)

# summary(complete.df$Ethnicity)
# summary(onlyFull.df$Ethnicity)
```
think about lag gdp as an instrument 

check minimum wage thing

check correlation of standard errors/selection of variables

show examples of plots

## Variable Selection

```{r}
fixed_vcovHC1 = coeftest(fixed, vcov. = vcovHC)
fixed_vcovHC1
```

```{r}
fixed1.coefs = names(coef(fixed))

linearHypothesis(model = fixed, c(coefs[grep("Ethnicity", coefs)],coefs[grep("GDP", coefs)], "lagInflationTax:v234", "lagInflationTax:I(v234^2)"), white.adust=T)
```

```{r}
fixed2 = update(fixed, . ~ . -Ethnicity -ChangeInGDP -ChangeInGDP:lagInflationTax -ChangeInGDP:lagChangeInGDP 
                -lagChangeInGDP -lagChangeInGDP:lagInflationTax -Ethnicity:lagInflationTax 
                -lagInflationTax:v234 -lagInflationTax:I(v234^2))
summary(fixed2)
fixed_vcovHC2 = coeftest(fixed2, vcov. = vcovHC)
fixed_vcovHC2

```

