---
title: "Analysis"
author: "Pedro Girardi"
date: "January 27, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages}
library(tidyverse)
library(data.table)
library(lme4)
library(plm)
library(lmtest)
library(sandwich)
library(car)
```

## Importing df

```{r}
complete.df = fread("complete.csv")
colnames(complete.df)[c(1,7,5,4)] = c("State", "Age", "Nominal Income","Month")
complete.df$State = as.factor(complete.df$State)
levels(complete.df$State)[5]="São Paulo"
```

## Recoding Variables

Variables:

v203: Gender (Male=1)
v208: Ethnicity (White=1, Black=2, Yellow=3, Mixed=4, Native=5, Ignored=9)
v4191: Income (999999999 = ignored)
v301: Writes/reads? (Yes=1, No=2, 0="Deleted by the surveyer", NA=NA)
v307: schooling (a mess...)/turn into factor
v234: age

ADD 409 (TYPE OF WORKER!!!!)

```{r}
complete.df = complete.df %>% mutate(Gender = as.factor(v203),
                       Ethnicity = as.factor(v208),
                       Literacy = as.factor(v301),
                       Schooling = as.factor(v307),
                       EmploymentType = as.factor(v409),
                       idind = as.factor(idind)) %>% 
                              select(-v040, -v050, -v203, -v208, -v301, -v307, -v409,
                                     -starts_with("vD"))
complete.df$Schooling = as.factor(ifelse(is.na(complete.df$Schooling), "NoSchooling", complete.df$Schooling))
levels(complete.df$Gender) = c("Male", "Female")
levels(complete.df$Ethnicity) = c("White", "Black", "Yellow", "Mixed", "Native", "Ignored")
levels(complete.df$Literacy) = c("Yes", "No")
levels(complete.df$Schooling) = c("Primary", "HighSchool_1", "HighSchool_2",
                                  "MiddleSchool", "HighSchool_3", "College",
                                  "AdultsSchool", "PreSchool", "Graduate",
                                  "NoSchooling")
levels(complete.df$EmploymentType) = c("Domestic", "Employee") #note that people who own their own business don't report income
```

## Visually checking for mixed effects

```{r, cache=T, eval=F}
set.seed(2)
ggplot(complete.df %>% filter(idind %in% sample(complete.df$idind, size = 25)),
       aes(x=lagInflationTax, y=realWage)) +
  geom_point(aes(col=idind)) +
  geom_smooth(aes(col=idind), method = "lm", se = F) +
  theme_minimal() +
  theme(legend.position="none")
```

## Fitting LME model

Worrying about LME not being the ideal. Needs to test with Hausman test.


```{r}
set.seed(1)
sampleInd = sample(complete.df$idind, size = length(complete.df$idind)/100)
sample_complete.df =  complete.df %>% filter(idind %in% sampleInd)
```

## be sure to test with hausman 

* remove people w fewer than 3 

* run hausmann test 

Decided not to have random effects for inflation coefficient so to avoid issues with hausmann test (trade-off)

Checked with Katie, sampling expert, on potential issues with subsetting and decided to subset (issue with power may exist, but mostly for very specific interactions)


```{r Fitting fixef}
fixed = plm(log(realWage) ~ lagInflationTax + ChangeInGDP * lagChangeInGDP + 
                (State +Gender + Ethnicity + Literacy +
                   Schooling + EmploymentType +
                   Age + I(Age^2) + as.factor(Month)+
                   veryVulnerable)*lagInflationTax,
            data = complete.df, index = c("idind"), model = "within") 

random = plm(log(realWage) ~ lagInflationTax + ChangeInGDP * lagChangeInGDP + 
                (State +Gender + Ethnicity + Literacy +
                   Schooling + EmploymentType +
                   Age + I(Age^2) + as.factor(Month)+
                   veryVulnerable)*lagInflationTax,
            data = complete.df, index = c("idind"), model = "random") 
```

```{r}
summary(fixed)
# summary(random)
```

```{r}
phtest(fixed, random)

# summary(complete.df$Ethnicity)
# summary(onlyFull.df$Ethnicity)
```
think about lag gdp as an instrument 

check minimum wage thing

check correlation of standard errors/selection of variables

show examples of plots

## Variable Selection

```{r}
fixed_vcovHC1 = coeftest(fixed, vcov. = vcovHC)
fixed_vcovHC1
```

```{r}
coefs = names(coef(fixed))
linearHypothesis(model = fixed, c(coefs[grep("Ethnicity", coefs)],coefs[grep("GDP", coefs)], "lagInflationTax:Age", "lagInflationTax:I(Age^2)"), white.adust=T)
```

```{r}
fixed2 = update(fixed, . ~ . -Ethnicity -ChangeInGDP -ChangeInGDP:lagInflationTax -ChangeInGDP:lagChangeInGDP 
                -lagChangeInGDP -lagChangeInGDP:lagInflationTax -Ethnicity:lagInflationTax 
                -lagInflationTax:Age -lagInflationTax:I(Age^2))
summary(fixed2)
fixed_vcovHC2 = coeftest(fixed2, vcov. = vcovHC)
fixed_vcovHC2
```

```{r}
coefs = names(coef(fixed2))
linearHypothesis(model = fixed2, c(coefs[grep("lagInflationTax:Gen", coefs)],coefs[grep("lagInflationTax:Lit", coefs)],coefs[grep("lagInflationTax:Emp", coefs)]), white.adust=T)
# maybe recode factors to have mid year vs rest?
```

```{r}
fixed3 = update(fixed2, . ~ . -lagInflationTax:Gender -lagInflationTax:Literacy -lagInflationTax:EmploymentType)
summary(fixed3)
fixed_vcovHC3 = coeftest(fixed3, vcov. = vcovHC)
fixed_vcovHC3
```

```{r}
coefs = names(coef(fixed2))
linearHypothesis(model = fixed3, c(coefs[grep("Tax:Sch", coefs)]), white.adust=T)
# maybe recode factors to have mid year vs rest?
# save.image("~/Comps/finalModels.RData")
stargazer(fixed_vcovHC3, 
          type = "latex", single.row = T, 
          dep.var.caption = "log(Real Wage)", 
          title = "Final Regression Model", font.size = "small")
```
