---
title: "Analysis"
author: "Pedro Girardi"
date: "January 27, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages}
library(tidyverse)
library(data.table)
library(lme4)
library(plm)
library(lmtest)
library(sandwich)
library(car)
library(xtable)
```

## Importing df

```{r}
complete.df = fread("complete_diffInDiff.csv")
colnames(complete.df)[c(1,7,5,4)] = c("State", "Age", "Nominal Income","Month")
complete.df$State = as.factor(complete.df$State)
levels(complete.df$State)[5]="São Paulo"
```

## Recoding Variables

Variables:

v203: Gender (Male=1)
v208: Ethnicity (White=1, Black=2, Yellow=3, Mixed=4, Native=5, Ignored=9)
v4191: Income (999999999 = ignored)
v301: Writes/reads? (Yes=1, No=2, 0="Deleted by the surveyer", NA=NA)
v307: schooling (a mess...)/turn into factor
v234: age

ADD 409 (TYPE OF WORKER!!!!)

```{r}
complete.df = complete.df %>% mutate(Gender = as.factor(v203),
                       Ethnicity = as.factor(v208),
                       Literacy = as.factor(v301),
                       Schooling = as.factor(v307),
                       EmploymentType = as.factor(v409),
                       idind = as.factor(idind)) %>% 
                              select(-v040, -v050, -v203, -v208, -v301, -v307, -v409,
                                     -starts_with("vD"))
complete.df$Schooling = as.factor(ifelse(is.na(complete.df$Schooling), "NoSchooling", complete.df$Schooling))
levels(complete.df$Gender) = c("Male", "Female")
levels(complete.df$Ethnicity) = c("White", "Black", "Yellow", "Mixed", "Native", "Ignored")
levels(complete.df$Literacy) = c("Yes", "No")
levels(complete.df$Schooling) = c("Primary", "HighSchool_1", "HighSchool_2",
                                  "MiddleSchool", "HighSchool_3", "College",
                                  "AdultsSchool", "PreSchool", "Graduate",
                                  "NoSchooling")
levels(complete.df$EmploymentType) = c("Domestic", "Employee") #note that people who own their own business don't report income
```

## Visually checking for mixed effects

```{r, cache=T, eval=F}
set.seed(2)
ggplot(complete.df %>% filter(idind %in% sample(complete.df$idind, size = 25)),
       aes(x=lagInflationTax, y=realWage)) +
  geom_point(aes(col=idind)) +
  geom_smooth(aes(col=idind), method = "lm", se = F) +
  theme_minimal() +
  theme(legend.position="none")
```

## Fitting LME model

Worrying about LME not being the ideal. Needs to test with Hausman test.


```{r}
set.seed(1)
sampleInd = sample(complete.df$idind, size = length(complete.df$idind)/100)
sample_complete.df =  complete.df %>% filter(idind %in% sampleInd)
```

## be sure to test with hausman 

* remove people w fewer than 3 

* run hausmann test 

Decided not to have random effects for inflation coefficient so to avoid issues with hausmann test (trade-off)

Checked with Katie, sampling expert, on potential issues with subsetting and decided to subset (issue with power may exist, but mostly for very specific interactions)


```{r Fitting fixef}
fixed = plm(realWage ~ PriceIndex + RealGDP + 
                (State +Gender + Ethnicity + Literacy +
                   Schooling + EmploymentType +
                   Age + I(Age^2) + as.factor(Month)+
                   veryVulnerable)*lagInflationTax -State -Gender -Ethnicity -veryVulnerable,
            data = sample_complete.df, index = c("idind", "timeDiscrete"), model = "fd") 
```

```{r}
summary(fixed)
```

## Variable Selection

```{r}
fixed_vcovHC1 = coeftest(fixed, vcov. = vcovHC)
fixed_vcovHC1
```

```{r}
coefs = names(coef(fixed))
linearHypothesis(model = fixed, c(coefs[grep("Ethnicity", coefs)],coefs[grep("GDP", coefs)], "lagInflationTax:Age", "lagInflationTax:I(Age^2)"), white.adust=T)
```

```{r}
fixed2 = update(fixed, . ~ . -Ethnicity -ChangeInGDP -ChangeInGDP:lagInflationTax -ChangeInGDP:lagChangeInGDP 
                -lagChangeInGDP -lagChangeInGDP:lagInflationTax -Ethnicity:lagInflationTax 
                -lagInflationTax:Age -lagInflationTax:I(Age^2))
summary(fixed2)
fixed_vcovHC2 = coeftest(fixed2, vcov. = vcovHC)
fixed_vcovHC2
```

```{r}
coefs = names(coef(fixed2))
linearHypothesis(model = fixed2, c(coefs[grep("lagInflationTax:Gen", coefs)],coefs[grep("lagInflationTax:Lit", coefs)],coefs[grep("lagInflationTax:Emp", coefs)]), white.adust=T)
# maybe recode factors to have mid year vs rest?
```

```{r}
fixed3 = update(fixed2, . ~ . -lagInflationTax:Gender -lagInflationTax:Literacy -lagInflationTax:EmploymentType)
summary(fixed3)
fixed_vcovHC3 = coeftest(fixed3, vcov. = vcovHC)
fixed_vcovHC3
```

```{r}
coefs = names(coef(fixed2))
linearHypothesis(model = fixed3, c(coefs[grep("Tax:Sch", coefs)]), white.adust=T)
# maybe recode factors to have mid year vs rest?
# save.image("~/Comps/finalModels.RData")
```


```{r}
stargazer(fixed_vcovHC3, 
          type = "latex", single.row = T, 
          dep.var.caption = "log(Real Wage)", 
          title = "Final Regression Model", font.size = "small")
```

```{r}
# CIs for 1% month inflation tax?

coefs.fixed3 = data.frame(sumCoefs = c(sum(fixed3$coefficients[c(1)]), #base
sum(fixed3$coefficients[c(1,39)]), #base no shooling
sum(fixed3$coefficients[c(1,39,51)]), #base no shooling, vulnerable
sum(fixed3$coefficients[c(1,28)]), #base, RJ
sum(fixed3$coefficients[c(1,39,28)]), #base no shooling, RJ
sum(fixed3$coefficients[c(1,39,51,28)]) #base no shooling, vulnerable, RJ
))

coefs.fixed3 = coefs.fixed3 %>% 
  mutate(change_01pct = round((exp(sumCoefs/1000)-1)*100, 2),
         change_1pct = round((exp(sumCoefs/100)-1)*100, 2),
         change_3pct = round((exp(sumCoefs/100*3)-1)*100, 2),
         DemographicGroup = c("Base",
                              "Base with no schooling",
                              "Base no schooling, very vulnerable",
                              "Base, RJ",
                              "Base, RJ, no schooling",
                              "Base, RJ, no schooling, vulnerable"))
coefs.fixed3 = coefs.fixed3[,c(5,2,3,4)]
print.xtable(xtable(coefs.fixed3, caption = c("Changes in Income for Demographic Groups")),
             include.rownames=F)

# a = pvcovHC(fixed3, method = "white2", type="HC1", "group")
```

```{r, eval = F}
# creates vcov narrow table
fixed3_interactionCoefs = names(fixed3$coefficients[-c(2:25)])
reduced_vcov3 = vcov_fixed3[fixed3_interactionCoefs,fixed3_interactionCoefs]
reduced_vcov3 = data.frame(row.names = rownames(reduced_vcov3),
                              typeFactor = c("Base", rep("State",5), rep("Schooling", 9), rep("Month", 11), "veryVulnerable"),
                              numberFactor = as.integer(c(1, 1:5, 1:9, 1:11, 1)),
                              reduced_vcov3) %>%
  rownames_to_column() %>%
  tidyr::gather(key = "key", value="value", -c(1,2,3))

# creates data frame with all 1440 cases
cases.df = data.frame(Base = rep(1, 1440),
           State = rep(0:5, 1440/6),
           Schooling = rep(rep(0:9, each=6),1440/(6*10)),
           Month = rep(rep(rep(0:11, each=10), each=6), 1440/(6*10*12)),
           veryVulnerable = rep(0:1, each=720))

coefSE = 

```

```{r}
# create matrix with all interaction terms
vcovInteractions = vcov_fixed3[-c(2:25), -c(2:25)]
infCoefs = fixed3$coefficients[-c(2:25)]

# find all possible combos
stateIndex = c(0,2:6)
educIndex = c(0,7:15)
monthIndex = c(0,16:26)
vulnerableIndex = c(0,27)

# length(stateIndex)*length(educIndex)*length(monthIndex)*length(vulnerableIndex) # length checks ok 1440
# create DF with all possible combos
cases.df = data.frame(Base = rep(1, 1440),
           State = rep(stateIndex, 1440/6),
           Schooling = rep(rep(educIndex, each=6),1440/(6*10)),
           Month = rep(rep(rep(monthIndex, each=10), each=6), 1440/(6*10*12)),
           veryVulnerable = rep(0:1, each=720))

# loop over all possible coefficient combos
covarianceValues = double(length=nrow(cases.df))
coefficientEstimates = covarianceValues+fixed3$coefficients[1]

          for (i in 1:nrow(cases.df[,])){
          filteredVcov = vcovInteractions
          
          if(cases.df$veryVulnerable[i]==0){
                 filteredVcov = filteredVcov[-27,-27]}else{
                   coefficientEstimates[i]=coefficientEstimates[i]+infCoefs[27]
                 }

      indexRed = monthIndex[monthIndex!=cases.df$Month[i]]
      if (cases.df$Month[i]!=0) {
        filteredVcov = filteredVcov[-indexRed, -indexRed]
        coefficientEstimates[i]=coefficientEstimates[i]+infCoefs[cases.df$Month[i]]
      } else {
        filteredVcov = filteredVcov[-monthIndex[-1],-monthIndex[-1]]
      }

    indexRed = educIndex[educIndex!=cases.df$Schooling[i]]
    if (cases.df$Schooling[i]!=0) {
      filteredVcov = filteredVcov[-indexRed, -indexRed]
      coefficientEstimates[i]=coefficientEstimates[i]+infCoefs[cases.df$Schooling[i]]
    } else {
      filteredVcov = filteredVcov[-educIndex[-1],-educIndex[-1]]
    }

  indexRed = stateIndex[stateIndex!=cases.df$State[i]]
  if (cases.df$State[i]!=0) {
    filteredVcov = filteredVcov[-indexRed, -indexRed]
    coefficientEstimates[i]=coefficientEstimates[i]+infCoefs[cases.df$State[i]]
  } else {
    filteredVcov = filteredVcov[-stateIndex[-1],-stateIndex[-1]]
  }
  covarianceValues[i]=sum(filteredVcov)
  
  
}

cases.df$covarianceValues = covarianceValues
cases.df$se = sqrt(cases.df$covarianceValues)
cases.df$coef = coefficientEstimates
cases.df = cases.df %>%
  arrange(coef) %>%
  mutate(case = 1:1440)
```

```{r}
hist(cases.df$coef)
plot_Final1 = cases.df %>%
  filter(se<2) %>%
  mutate(veryVulnerable = ifelse(veryVulnerable==1,"Yes","No"),
         Significantly = ifelse(coef+1.96*se<0,"Negative", 
                                ifelse(coef-1.96*se>0, "Positive", "None"))) %>% 
  ggplot(aes(y=case)) +
  geom_line(aes(x=coef)) +
  geom_errorbarh(aes(y=case,
                     xmin=coef-1.96*se,
                     xmax=coef+1.96*se,
                     col=Significantly), alpha=.2) +
  geom_vline(xintercept = 0, alpha=.5, linetype = "longdash") +
  labs(x="Coefficient of inflation tax", 
       y="Cases") +
  theme_minimal()
ggsave(plot_Final1, filename = "Plots/plotFinal.jpeg", width = 6, height=6, units="in")

plot_Final2 = cases.df %>%
  mutate(veryVulnerable = ifelse(veryVulnerable==1,"Yes","No"),
         Significantly = ifelse(coef+1.96*se<0,"Negative", 
                                ifelse(coef-1.96*se>0, "Positive", "None"))) %>% 
  ggplot(aes(y=case)) +
  geom_line(aes(x=coef)) +
  geom_errorbarh(aes(y=case,
                     xmin=coef-1.96*se,
                     xmax=coef+1.96*se,
                     col=Significantly), alpha=.2) +
  geom_vline(xintercept = 0, alpha=.5, linetype = "longdash") +
  labs(x="Coefficient of inflation tax", 
       y="Cases") +
  theme_minimal()
ggsave(plot_Final2, filename = "Plots/plotFinal2.jpeg", width = 6, height=6, units="in")
  
```
use pvcovhc for shit!!!

```{r}
cases_final = cases.df %>%
    mutate(veryVulnerable = ifelse(veryVulnerable==1,"Yes","No"),
           Significantly = ifelse(coef+1.96*se<0,"Negative", 
                                  ifelse(coef-1.96*se>0, "Positive", "None")))
summary(as.factor(cases_final$Significantly))/sum(summary(as.factor(cases_final$Significantly)))
```